Ground state energy of quantum dots using the coupled cluster method

### 2018-04-10 project_2/article/article.tex
Add section on second quantization

@@

>>>>

\newcommand{\acr}[1]{a_{#1}^{\dagger}}
\newcommand{\ade}[1]{a_{#1}}

@@

    \subsection{Second quantization}
        We now move over to a use second quantization. Employing the creation
        operators, $\acr{p}$, and the destruction operators, $\ade{p}$, we can
        write the Hamiltonian as
        \begin{align}
            H
            &=
            \sum_{pq}h_{q}^{p}\acr{p}\ade{q}
            + \sum_{pqrs}w_{rs}^{pq}\acr{p}\acr{q}\ade{s}\ade{r},
        \end{align}
        where the sums are general indices over all $L$ basis states and the
        matrix elements are defined as
        \begin{gather}
            h^{p}_{q} \equiv \bra{p}h\ket{q}, \\
            w_{rs}^{pq} \equiv \bra{pq}v\ket{rs}.
        \end{gather}
        In the case of the eigenstates we have that the one-body operator
        reduces to a diagonal matrix.
        \begin{align}
            h^{p}_{q}
            &= \bra{p}h\ket{q}
            = \varepsilon_q\braket{p}{q}
            = \varepsilon_q\delta_{pq},
        \end{align}
        where $\delta_{pq}$ is the Kronecker-Delta.
